\vskip-0.6in \Large Political Uncertainty

### 2016-02-09 two-groups.tex
save GS-extension as two-groups for model with two interest groups

\section{Our Extension to Uncertainty}
\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

Discrete version (Conversation between Kristy and Frank, 3/27/15)
	\item Purpose: try to understand what the right objective function is. Does maximizing total probability also maximize the probability of winning?

@@

	\item Frank prefers to write

@@

				\item Note that, in a probit we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$

@@

		Assuming $\ve \sim N(0,1)$, the probability that legislator $z$ votes ``no'' is $\Phi\left(\beta z - \alpha + b(z) \right)$
	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. Then the three probabilities are

@@

			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)$, $\Phi\left(- \alpha + b(0) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)$

@@

				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \Phi\left(\beta z - \alpha + b(z) \right)

@@

					W_B \biggl[ \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\left(1-\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
			Substituting from the definition of $X$ but substituting Logit for Probit and using the shorthand notation on the top of page~\pageref{page:sh},

@@

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is (in terms of probit)
				\begin{multline}
					W_B \biggl[ \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
				\end{multline}
			Simplifying:
			\begin{multline}
					W_B \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \biggl[ \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
					\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - 
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
				\end{multline}
			Simplifying further:
			  \begin{multline}
					\Phi\left(- \alpha + b(0) \right)+ \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\right)^2}{2}} }
					\label{eq:firstfoc}
				\end{multline}

			The two symmetric conditions would be:
			\begin{multline}
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
				\end{multline}
			\begin{multline}
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
				\end{multline}
		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
			\item Need to check SOC at some point
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
		\end{itemize}
	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
		\begin{equation}
					\frac{1}{1+e^{\alpha - b(0)}} + \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }}
					- 2\frac{1}{1+e^{\alpha - b(0)}}  \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)} }
					\label{eq:logistic}
				\end{equation}
		\begin{itemize}
			\item A LOT of math (I will put it somewhere else) leads to three equations:
				\[
				  \left[ - \alpha + b(0) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] + \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] =\left[ - \alpha + b(0) \right]+ \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] +\left[ - \alpha + b(0) \right]
				\]
			\item A little more math implies that all three quantities in brackets must equal zero
				\begin{itemize}
					\item That is, Vote Buyer B's bribe should make each legislator just indifferent between the new proposal and the status quo
					\item First question: why doesn't this depend on willingness-to-pay?
						\begin{itemize}
							\item FOC says each bribe should be calibrated so that $W_B \cdot \text{marginal contribution to probability} = 1$, or $\frac{\partial \text{probability}}{\partial \text{bribe}} = \frac{1}{W_B}$
							\item Something happens when all three conditions come together...what's the intuition?
						\end{itemize}
					\item To do next: see what non-negativity of bribes implies
						\begin{itemize}
							\item Also, insert Vote Buyer A's behavior
							\item And give the various legislators different variances
						\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.

>>>>

\vskip.3in
\section{Our Extension to Uncertainty}
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

@@

	\item We write

@@

				\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$

@@

		Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}$. 
	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. For ease of notation, let
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
		\end{enumerate}
	\item Then the three probabilities are

@@

			\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$

@@

				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}

@@

@@

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
			\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.

		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\end{itemize}

@@

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.
